Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-01 paper-ieee-trans.tex
added changes

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by the creation of software development and
e-Infrastructure coordination dedicated projects. This work examines the
evolution of the software engineering methodologies used in past and present
European-funded software projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the
foundation of the first project in 2001. In particular, we describe the team
organizational structure, techniques and procedures that have guided the Quality
Assurance definitions in order to deliver quality software. We highlight the challenges
and barriers that have been faced throughout these years and how to overcome them totally or
partially. To conclude, we discuss the future directions of software
Quality Assurance methodologies for the incoming projects.
\end{abstract}

@@

\IEEEPARstart{I}{n} the European scientific research arena, the analysis of
some of the last decade software development projects depicts a continuous
increase of the prominence and robustness of testing and validation procedures.
The observed trends are aligned with the evolution of the software engineering
techniques (e.g. rise of DevOps practices) over the last years. This is tied to
the parallel advancements in the ICT field (with virtualization and container
technologies) and the emergence of automation and event-response tools. In the
following, we introduce a set of European Commission funded projects that cover
2001 up to now, where the authors of this summary were and are currently
involved. For each project we explain how they addressed the challenge in
software reliability.

\section{Evolution of research on software reliability in EU-projects}

@@

\section{New Trends in Software Reliability}

@@

\section{Conclusion}

@@

>>>>

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by the creation of software development and
e-Infrastructure coordination dedicated projects. This work examines the
evolution of the software engineering methodologies used in past and present
European Commission-funded software projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the
foundation of the first project in 2001. In particular, we describe the team
organizational structure, techniques and procedures that have guided the Quality
Assurance definitions in order to deliver quality software. We highlight the challenges
and barriers that have been faced throughout these years and how to overcome them totally or
partially. To conclude, we discuss the future directions of software
Quality Assurance methodologies for the incoming projects.
\end{abstract}

@@

\IEEEPARstart{I}{n} the European scientific research arena, the analysis of
some of the last decade software development projects depicts a continuous
increase of the prominence and robustness of testing and validation procedures.
The observed trends are aligned with the evolution of the software engineering
techniques (e.g. rise of DevOps practices \cite{zhu}) over the last years. This is tied to
the parallel advancements in the ICT field (with virtualization and container
technologies) and the emergence of automation and event-response tools.

In this paper, we introduce a set of European Commission (EC)-funded projects that goes from
2001 up to now, where the authors of this summary were and are currently
involved. For each project, we explain how they addressed the challenge in
software reliability. Furthermore, we detail new trends in software reliability.

The reminder of this paper is organized as follows. Section \ref{sec:ev} details the evolution of research on software reliability in EC-projects. Section \ref{sec:ntsr} provides information about new research trends in software reliability. Finally, Section \ref{sec:con} concludes.

\section{Evolution of research on software reliability in EC-projects}
\label{sec:ev}

@@

\section{New trends in software reliability}
\label{sec:ntsr}

@@

\section{Conclusion}
\label{sec:con}

@@

\bibitem{zhu}
L. Zhu and L. Bass and G. Champlin-Scharff, \emph{DevOps and Its Practices}, 
IEEE Software, vol. 33, no. 3, pp. 32--34, May-June 2016.
